Figures

### 2020-10-09 inst/manuscript/figures.Rmd
Drafted cropland maps panel 1 figure; divided up and renamed data_from_segmenter into different scripts for doing area stats comparisons between validation polygons and segments at grid, tile, and aoi scales

>>>>

### Figure 8: Cropland maps
```{r, eval=FALSE}
library(stars)
library(ggplot2)
library(aws.s3)
library(RStoolbox)
library(cowplot)

segment_files <- dir(here("external/data/results/segments/merged"),
                     pattern = "boundarymerge", full.names = TRUE)
iid <- as.numeric(gsub("[[:alpha:]]|_|\\.", "", basename(segment_files)))
segment_files <- tibble(file = segment_files, order = iid) %>% arrange(iid)
segment_files <- segment_files %>% filter(!grepl("aoi3_*.*merge.geojson", file))

fdensity <- stars::read_stars(
  system.file("extdata", "field_density005.tif", package = "activemapper")
)

# OS images
osimgs <- get_bucket_df(
  bucket = "activemapper", prefix = "planet/composite_sr_buf_fix/OS/", max = Inf
) %>% as_tibble %>% select(Key)

# example tiles
# aoi 1: tile 486794
# aoi 5: tile 539730
# aoi 11: 
# aoi 15:

flds_1 <- read_sf(segment_files$file[1])
flds_5 <- read_sf(segment_files$file[5])
flds_11 <- read_sf(segment_files$file[11])
flds_15 <- read_sf(segment_files$file[15])

tile_ss <- tiles %>% filter(tile %in% c(486794, 539730, 591243, 616490))
# ggplot(aois %>% filter(aois == 1)) + geom_sf() + 
#   geom_sf(data = tile_ss)
flds_tile1 <- flds_1 %>% filter(st_intersects(., tile_ss[1, ], sparse = FALSE))
flds_tile2 <- flds_5 %>% filter(st_intersects(., tile_ss[2, ], sparse = FALSE))
flds_tile3 <- flds_11 %>% filter(st_intersects(., tile_ss[3, ], sparse = FALSE))
flds_tile4 <- flds_15 %>% filter(st_intersects(., tile_ss[4, ], sparse = FALSE))

impath <- osimgs %>% 
  filter(grepl(paste0(tile_ss$tile, collapse = "|"), Key)) %>% 
  mutate(pth = paste0("/vsis3/activemapper/", Key)) %>% pull(pth)

# img <- read_stars(impath)
# mxval <- st_apply(img, 3, max) %>% pull(max)
# imgngb <- st_rgb(img[, , , 4:2], 3, maxColorValue = mxval[4:2])

fld_tiles <- list(flds_tile1, flds_tile2, flds_tile3, flds_tile4)
isets <- lapply(1:4, function(x) {
  imgr <- brick(impath[x])[[2:4]]
  xylims <- st_bbox(imgr)
  iset <- ggplot() + 
    ggRGB(imgr, maxpixels = 50000, stretch = "lin", ggLayer = TRUE) +
    geom_sf(data = fld_tiles[[x]], fill = "transparent", color = "yellow", 
            size = 0.2) + 
    geom_sf(data = tile_ss[x, ], color = "red", fill = "transparent") + 
    scale_x_continuous(expand = c(0, 0)) + 
    scale_y_continuous(expand = c(0, 0)) + 
    coord_sf(xlim = xylims[c(1, 3)], ylim = xylims[c(2, 4)]) + 
    theme_void()
})
isets[[2]]

# Main map
xylims <- st_coordinates(ghana)
# twk <- diff(range(xylims[, 1])) * 0.05
maprange <-  c(range(xylims[, 1]) + c(-1.25, 1.25), 
               range(xylims[, 2]))

inset_cols <- c("red", "orange", "pink", "brown")
p <- ggplot(africa) + 
  geom_sf(fill = "gray40", color = "grey", size = 0.25) +  
  geom_stars(data = fdensity * 100) +
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") +
  geom_sf(data = tile_ss, fill = "red", col = "red") +
  scale_fill_viridis_c(name = "% cover", na.value = "transparent") +
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) + 
  theme_void() + 
  theme(legend.position = "bottom", 
        legend.text = element_text(colour = "white"), 
        legend.title = element_text(colour = "white"))

inset_map <- ggdraw() +
  draw_plot(p) +
  draw_plot(isets[[1]], x = 0.07, y = 0.77, width = 0.2, height = 0.2) + 
  draw_plot(isets[[2]], x = 0.72, y = 0.6, width = 0.2, height = 0.2) + 
  draw_plot(isets[[3]], x = 0.04, y = 0.37, width = 0.2, height = 0.2) + 
  draw_plot(isets[[4]], x = 0.76, y = 0.25, width = 0.2, height = 0.2)

ggsave(filename = here("presentations/figures/cropcover_with_insets.png"), 
       plot = inset_map, bg = "transparent", width = diff(maprange[1:2]), 
       height = diff(maprange[3:4]), units = "in", dpi = 300)

  # geom_stars(data = imgngb) + scale_fill_identity()
  # geom_sf(data = flds_tile)

plot(flds_tile[1])

fboundary <- read_sf(segment_files$file[1])

pal <- RColorBrewer::brewer.pal(n = 9, "Spectral")[c(1, 2, 3, 4, 9)]

# Panels, organized top to bottom
# Panel 1: Cropland probabilities, with 3 m probability side maps (tiles)
p <- ggplot(africa) + 
  geom_sf(fill = "gray97", color = "grey", size = 0.25) +  
  geom_stars(data = fdensity * 100) + 
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") + 
  scale_fill_viridis_c(name = "% cover", na.value = "transparent") + 
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) + 
  theme_void()

# Panel 2: Cropland cover, with polygon side maps over composites (tiles)
p <- ggplot(africa) + 
  geom_sf(fill = "gray97", color = "grey", size = 0.25) +  
  geom_stars(data = fdensity * 100) + 
  geom_sf(data = aois, size = 0.1, fill = "transparent", col = "grey") + 
  geom_sf(data = tile_ss, fill = "red", col = "red") + 
  scale_fill_viridis_c(name = "% cover", na.value = "transparent") + 
  coord_sf(xlim = maprange[1:2], ylim = maprange[3:4]) + 
  theme_void()
p

# Panel 3: Average field size (kriging adjusted?),

# Panel 4: Field number (kriging adjusted)
